### 2016-09-05 Manuscript/SW_early_life_telomeres_tables_and_figures.Rmd
More edits

#Run the model
lm2 <- lmer(CqTelomere ~  LogAge* (Helper)+Tarsus + NonHelper + Sex + BodyMass  +yday*LogAge + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=yday,
       col = (Ageclass))) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth()+
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')

>>>>

#Run the model
lm2 <- lmer(CqTelomere ~  LogAge+Tarsus + NonHelper + Sex + BodyMass  +yday + (1|FieldPeriodID) + (1|BirdID) + (1|TerritoryID),
            data = temp,
            REML = FALSE)
lm2 <- standardize(lm2)
#Model averaging

@@

temp <- subset(juv_r,Season == 'Major')
Fig3C <- ggplot(temp,
       aes(
           y = RTL,
           x=yday,
       col = (Ageclass))) +
  theme_classic() +
  theme(axis.text.x = element_text(size = 12), 
        axis.text.y = element_text(size = 12), 
        axis.title.y = element_text(size = 14,vjust=0.8),
        axis.title.x = element_text(size = 14),
                axis.line.x = element_line(colour = 'black'),
        axis.line.y = element_line(colour = 'black'),
        legend.position = 'top') +
  geom_point()+
   stat_smooth(method = 'lm',formula = y~poly(x,2))+
  # scale_colour_manual(values = c('grey','darkorange','darkgreen'))+
  # scale_fill_manual(values = c('grey','darkorange','darkgreen'))+
  annotate('text',x = 3,y = 2.1,label = 'C')
